Agile Monitoring of Evolving Web Services: For the Little Man

### 2018-04-08 related-work.tex
rel

>>>>

In their work Baresi and Guinea have proposed the Multi-layer Collection and Constraint Language (mlCCL) which allows them to define how to collect, aggregate, and analyze runtime data in a multi-layered system. They also present ECoWare, a framework for event correlation and aggregation that supports mlCCL, and provides a dashboard for on-line and off-line drill-down analyses of collected data \cite{Bare13-monitoring}.
